The Spine of American Legal Practice

### 2016-06-28 article/article.Rmd
Make the network graph look better

```{r code-to-code-network, fig.width=12, fig.height=12, fig.cap = "The structure of borrowings among nineteenth-century codes of civil procedure. Note that several versions of New York's Field Code were at the center of the network, while other states such as California and Ohio became centers of regional variations on the Field Code."}
ggraph(codes_g, "igraph", algorithm = "nicely") +
  geom_edge_fan(aes(edge_width = sections_borrowed, 
                    alpha = sections_borrowed),
                arrow = arrow(type = "closed", ends = "first",
                              length = unit(0.20, "inches"),
                              angle = 15)) +
  geom_node_point(aes(colour = as.factor(distance)), size = 10) +
  scale_edge_width("Sections borrowed", range = c(1, 2), guide = "none") + 
  scale_edge_alpha(range = c(0.3, 0.6), guide = "none") +
  scale_color_discrete("Distance from a NY code") +
  ggforce::theme_no_axes() +
  geom_node_text(aes(label = name), size = 6) +
  labs(title = "The migration of law through borrowings in nineteenth-century codes of civil procedure") +
  theme(legend.position = "bottom",
        panel.border = element_blank())
```

>>>>

```{r code-to-code-network, fig.width=6.5, fig.height=7, fig.cap = "The structure of borrowings among nineteenth-century codes of civil procedure. Note that several versions of New York's Field Code were at the center of the network, while other states such as California and Ohio became centers of regional variations on the Field Code."}
set.seed(3728)
ggraph(codes_g, "igraph", algorithm = "nicely") +
  geom_edge_fan(aes(edge_width = sections_borrowed, 
                    alpha = sections_borrowed),
                arrow = arrow(type = "closed", ends = "first",
                              length = unit(0.20, "inches"),
                              angle = 15)) +
  geom_node_point(aes(colour = as.factor(distance)), size = 5) +
  scale_edge_width("Sections borrowed", range = c(1, 2), guide = "none") + 
  scale_edge_alpha(range = c(0.3, 0.6), guide = "none") +
  scale_color_discrete("Distance from a NY code") +
  ggforce::theme_no_axes() +
  geom_node_text(aes(label = name), size = 3, family = "Palatino") +
  labs(title = "The migration of the Field Code",
       subtitle = "Codes of civil procedure connected by borrowed sections") +
  theme(legend.position = "bottom",
        panel.border = element_blank(),
        text = element_text(family = "Palatino"),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 8))
```
